### 2017-10-19 Risk analysis/Text/Layout/Layout/chapter2_methods.tex
Tried to implement juxtaposition test, not working, yet!

		\subsection{Implementation of reservoir-related likelihoods in the 3D model}

>>>>

		\subsection{Implementation of reservoir-related likelihoods in the 3D model}
		As for the 1D case before, for the 3D case it is assumed that additional information is provided in the form of layers thickness likelihoods. In this geological scenario, the information might have been gained for example from additional seismic obersavtions or from core sample data from a well nearby. Assuming a possible correlation with the layers in our model section, layer thickness likelihoods can be deduced respectively.\\
		First of all, a method to determine layer thicknesses in our model realizations has to be introduced. Here,
